%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Account Manager, Retail Americas lcs, Mercado Libre Latam} % Job title
    {Google LLC} % Organization
    {Buenos Aires, Argentina} % Location
    {Oct. 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mercado Libre is the biggest retail marketplace in LATAM region. I describe my role as an Analytical Account Manager, finding insights and data-driven marketing solutions for my client.}
        \item {Led measurement and testing workflow in order to validate business hypotheses (GeoX, Conversion Lift, Draft and Experiments, Causal Impact, Video experiments).}
        \item {Led conversations with different stakeholders like PMs, Product specialists, Customer Solution Engineers, Analytical Leads, executive, optimization and support teams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Account Strategist Latam} % Job title
    {Google LLC} % Organization
    {Buenos Aires, Argentina} % Location
    {Mar. 2017 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Expanded complex industry analysis such as Industry benchmarks, analysis of advertisers investment in different markets, budget forecasting and data-driven performance optimizations, specially for Amazon and many retail clients in the region.}
        \item {Developed a PLX, Data Studio dashboard which helps team reduce operating time in 75 percent, usage of +3500 sessions p/month.}
        \item {Prepared more than 100 high impact Google Ads optimizations across a wide range of Google products: Search, YouTube, Display, Apps.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Account Strategist Intern} % Job title
    {Google LLC Internship} % Organization
    {Buenos Aires, Argentina} % Location
    {Jul. 2016 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an Excel Macro Automation which makes an internal keyword categorization process 20 more efficient.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Business Consultant} % Job title
    {Paradigma Solutions Inc.} % Organization
    {Buenos Aires, Argentina} % Location
    {Nov. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in the process optimization of credit card deliveries, decreasing delivery issues ratios from 40 percent to 10 percent.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
